\section{Current implementation}

The code source of the current implementation is as always available on our GitHub repository at \url{https://github.com/fthuin/software_engineering_project} (you have to be logged in to see the content) and an online version is available on \url{asmae.herokuapp.com}. As there are thousands lines of code, we will describe the recently added features in this section.

\subsection{Player}

As the client requested during the meeting, staff member can now see if a player is linked to a pair in their interface and pairs are now automatically linked to a tournament after registration, depending on the pair properties of course.

This is allowed by our new TounoiCategorie class which record the various age related criteria necessary to make a decision and our TounoiTitle class which record the gender both player can have (man only, women only or mixed).

\subsection{Tournament}

It is now possible to modify the date of a tournament as well as to affect it to a category (double homme, double femme, double mix, tournoi des familles, ...). The category of a tournament will determine the rule a pair has to respect to join it (no mixed genre pair on double homme and double femme tournament, familly tournament under 15 years old, ...). The staff's tournament tab's design has also been fully reworked to be more intuitive and functional.

\subsection{Inscription fee}

To satisfy the needs of the client, we added a gestion of the basic inscription fee which must be payed by everyone and regrouped it with the previously implemented extras management. Staff member can now also see how much people paid for each extra under this new inscription tab.

\subsection{History}

As requested by the user we have added an \enquote{Historique} widget under players and courts as to simplify the staff's jobs and make the website more practical for their use. They can now have all the relevant information on the same page.

\subsection{PDF}

Once again, as requested by the user during our meeting, we have modified our pdf generation to centralize all the information of the court and player on the poule pdf. Allowing staff member to easily print the data and hand it to the player as needed.

\subsection{Database}

On the database side we now added a button that will flush the database of all informations relative to a yearly set of tournament such as pairs. This allows staff member to easily reinitialise the database while safe-keeping important information such as user account, court information, encoded extras, ...

\subsection{Geolocalisation}

We made our google maps tool fully functional and it is now possible for staff member to easily locate any given court or players home's location on the website.