\section{Teamwork}

The following subsection were each writen by a group member and contains their unedited impression (except spelling mistakes, which have been removed) on the teamwork in our team. \newline

\subsection{Romain}
The overall teamwork of the group is really good: the workload is nicely
split between all the members for each sprint; the weekly meetings allow
us to evaluate the progress of the project; the group leader assures that
everything goes according to the initial planning, and everybody is ready to
help if something takes more time than expected. \newline

\subsection{Benjamin}

This project lets us work as a small team, in conditions that are closer to
the working world than any other academic project we had. The group has to
be very careful on the planning, but our team is capable of efficiently
splitting the work among the members until now. The work is accomplished,
and only external things, such as a bunch of unexpected work from other
courses, have a bad impact on our work flow for this project. \newline

Furthermore, the atmosphere of the group gives motivation to all of us:
everyone stays ready to help anyone, avoiding the group to stuck
indefinitely on a bug.

\subsection{Quentin}
We had a slow start for the first week of implementation. This is due to
some peoples of the group having to get familiar with the frameworks.
Beside that everybody on the group is willing to create a good website that
match the client's expectation. \newline

This is the largest project we have ever had and a great challenge to work
with a larger group of people. This allows us to get more familiar with
bigger projects that we will have to face after university.

\subsection{Zacharie}

Since we are at university, it is the first time we have to realize a
project with a such great team. This implies some difficulties to
coordinate everybody but overall the work is perfectly split and each
member perform his duties. \newline

The atmosphere of the group is rather good. The project manager assumes
thoroughly his role and I am confident in our abilities to carry out this
project.

\subsection{Alexandre}

For some of us, it is the first time we work together on a project. It has
provided a great advantage to the group, because we have quickly detected
the abilities of everyone. \newline

As a result, the tasks are fairly divided up, and the work is progressing
at an appropriate rate, all while having a very good atmosphere within the
group.

\subsection{Florian}

It is a significant amount of work to create a website in accordance to the
customer requirements. It is hard to have a global view on the project,
because the requirements hide many untold technical things on the desired
product. This can lead to some difficulties with regard to the workload
evaluation. Moreover, it is a challenge to manage a team of eight people,
especially as it is a first time for me. Fortunately, my
teammates are all qualified to help in (at least) one part of the workload for
each sprint, and everyone is pretty self-governing. \newline

The main difficulty so far is to push everyone to deliver his work part by
part (beginning by the structure and then producing a step-by-step
implementation; each time with a commit on the git) to ensure the progress
of the tasks and to help when other team members have free time.
Personally, I feel that everyone does what he can, despite the workload in
the first year of master which limits the time left for this project.\newline
\subsection{Cyril}

I have no problem with the team in general, everything is proceeding
smoothly along the way as everyone accomplish the task they have been given
flawlessly. In short, everything is close to perfect in the team in my
opinion and I hope it stays this way until the end of the project.

\subsection{Nicolas}

It is the first time for me that I have to deal with such a big group of
people to work with. The last time I had to do a big project, we were 4.
Now the members are doubled. At first I thought it would be incredibly
difficult to work together on the same project. But at the start of the
first sprint, we managed to divide the work very well. And we carried on
this work dividing success through all the sprint so far. I didn't know we
would be able to accomplish so much work. Even though we didn't deliver
everything we wanted on the last sprint, we are still proud of what we
developed and on time to deliver our final version. If we can continue on
this line of good work, we will deliver a very good product to the client.
