\section{Teamwork}
\label{sec:Teamwork}

Every member of the group has taken a part to each deliverable of the project.
If you have any question, you can always directly contact the related member of
team or the project manager (our email addresses are on the front page). \newline

Our development methodology was Agile with Scrum, so the communication has
been a very important component in achieving the current application.
The project manager, \textbf{Florian}, had the though task to coordinate the
team members, and to communicate with the client. He had to be the mediator of
the team, in addition to help making documents and implementing some parts of
the application. In particular, Florian is creator of tools to automatically
fill the database, the system behind every button to export to CSV, the
deployment of the online version of the website and the setup of the admin
interface.\newline

\textbf{Quentin} and \textbf{Nicolas} where the two members responsible for
the front-end and back-end respectively, being the two most experienced with
the framework \textit{Django}. They initiated the code, and implemented most
parts of the final application.\newline

Finally, \textbf{Cyril}, \textbf{Benjamin}, \textbf{Zacharie}, \textbf{Romain}
and \textbf{Alexandre} all had flexible roles during the development.
Their affected tasks depended thus on the current goals of the sprint and they
regularly changed roles during the project. Some role still stood-out, for example :

\begin{itemize}
\item Cyril implemented the mailing system  and the automatic ranking check system.
\item Benjamin is the creator of all the video clips.
\item Alexandre studied in depth the requirements, and designed the original mock-ups.
\item Benjamin, Zacharie, Romain, and Alexandre worked together to design the
processes to print the score board, create the groups, and manage the groups.
\end{itemize}
\bigskip

While they had no precise job of which they were responsible, they of course
weren't idle either and worked hard to meet the deadlines.\newline

This made our group rather flexible to react in time of need, because there was
always someone ready to help, and we could easily adapt the team to tackle any
problem that may occur. This brought us to this final application, which we
believe that we can be proud of it. \newline
