\section{Other considerations}

During the Q/A session with the clients, many clarifications on various requirements in the written customer specification have been given. The clients have mentioned how they used to create groups for the tournaments. Usually, there are 5 pairs of players per group on saturday and 6 pairs of players per group on sunday. The groups are relatively balanced in terms of levels. Besides, there is no other condition on who's the group leader than being a member of the group. He/she can be selected randomly among players in the group. \newline

For the family tournament, criteria such as level, age and gender must not be taken into account while forming groups. However, wishes from players still have to be considered.\newline

For the sunday tournaments too, clarifications have also been made. For each tournament category, five games per group will be played in the morning, while six games will be played in the afternoon. For the morning games, only the winner will be encoded on the website,
while during the afternoon the whole score sheet will be encoded. Then, the system will have deduce the winner from those score sheet. \newline

Another important thing to implement is to choose courts in order to minimize players footprint. In order to achieve that goal, courts will then carry over from one level of the tournament tree to the next, so that only half of the winning players will have to move while the other half will play on the same court again.
If a court is not used during a tournament, the customers also mentioned that the court owner should be told and thanked for providing the court, even tough it won't be used at all. As this procedure may be automatized, we may have to consider it in our program architecture, but not demand from the customer have been made at the moment, so this should not be a priority.
If many courts are available, the ones that are closer to HQ are more desirable. \newline

Aside from the tournaments, wishes from the customer on document generation have been clarified. Although PDF files were mentioned as printable documents, print the page from the web browser does the job as desired by the customer. At least, it eases the basic requirement for documents, and full PDF document generation can now be considered as an extension. \newline

Finally, for each group table, only the table itself must be generated in a printable format. Advertisement on any side of the document will be handled directly by the staff. Invitation to players must not be handled by the program: the staff does everything manually.